Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
final final

Therefore, we optimize $F_C$ using a genetic algorithm, which is inherently
capable of coping with the stochastic fitness function. In each iteration
of the algorithm, a generation $\mathcal{G}_t = \left\{ G_i~|~1\le i\le M\right\}$
of $M$ individuals (genotypes) is converted into a new one, $\mathcal{G}_{t+1}$,
according to the following scheme:
\begin{description}[itemsep=0ex, leftmargin=0pt, format=\normalfont]
 \item[1. Evaluation] The fitness $F_i = F_C(G_i)$ of each individual is
     measured using at least 50 samples (and adaptively more if the 
     $(F_i)_{1\le i\le N}$ are tightly spaced, to at most 100).
 \item[2. Selection] We choose $50\%$ of the most successful members of $G_t$ as survivors.
     With a small chance, a weaker generator can survive, in order to keep the gene pool more diverse.
\item[3. Reproduction] We then replace the $|G_t|/2$ elements that did not make
    it for the next generation by either \emph{mutating} or \emph{recombining} the 
    survivors and get $\mathcal{G}_{t+1}$. This means we either change
    a single parameter randomly or take two individuals and randomly choose
    for every parameter from which parent to take the value from.
\end{description}

@@

\begin{figure}
    {\footnotesize\input{pictures/freq_optimization}}
    \caption{
        Genetic optimization process of genotypes with Erdös-Renyi topology
        ($N=100$ fixed) for the challenges $C\ix{high}$ and $C\ix{low}$.
        In each figure, one can see the $50$ genotypes of every Generation
        (single dots) together with the respective mean values (thick
        lines). Figures (a) to (c) depict the evolution of the three
        parameters ($\gain$, $\feedback$, and $\ERprob$) being optimized,
        while figure (d) shows the development of the fitness values.
    }
    \label{fig:freq_optimization}
\end{figure}

@@

The fitness curve of $G\ix{high,ring}$ in figure \ref{fig:freqrange}
confirms, that though $G\ix{high}$ is still better for high frequencies due
to the strong feedback, the ring topology provides an improvement compared
to the Erdös-Renyi topology when optimizing for $C\ix{high}$.

>>>>

Therefore, we optimize $F_C$ using a genetic algorithm, which is inherently
capable of coping with the stochastic fitness function. In each iteration
of the algorithm, a generation $\mathcal{G}_t = \left\{ G_i~|~1\le i\le M\right\}$
of $M$ individuals (genotypes) is converted into a new one, $\mathcal{G}_{t+1}$,
according to the following scheme:
\begin{description}[itemsep=0ex, leftmargin=0pt, format=\normalfont]
 \item[1. Evaluation] The fitness $F_i = F_C(G_i)$ of each individual is
     measured using at least 50 samples (and adaptively more if the 
     $(F_i)_{1\le i\le N}$ are tightly spaced, to at most 100).
 \item[2. Selection] We choose $50\%$ of the most successful members of $G_t$ as survivors.
     With a small chance, a weaker generator can survive, in order to keep the gene pool more diverse.
\item[3. Reproduction] We then replace the $|G_t|/2$ elements that did not make
    it for the next generation by either \emph{mutating} or \emph{recombining} the 
    survivors and get $\mathcal{G}_{t+1}$. This means we either change
    a single parameter randomly or take two individuals and randomly choose
    for every parameter from which parent to take the value.
\end{description}

@@

\begin{figure}
    {\footnotesize\input{pictures/freq_optimization}}
    \caption{
        Genetic optimization process of genotypes with Erdös-Renyi topology
        ($N=100$ fixed) for the challenges $C\ix{high}$ and $C\ix{low}$.
        In each figure, one can see the $50$ genotypes of every generation
        (single dots) together with the respective mean values (thick
        lines). Figures (a) to (c) depict the evolution of the three
        parameters ($\gain$, $\feedback$, and $\ERprob$) being optimized,
        while figure (d) shows the development of the fitness values.
    }
    \label{fig:freq_optimization}
\end{figure}

@@

The fitness curve of $G\ix{high,ring}$ in FIG. \ref{fig:freqrange}
confirms, that though $G\ix{high}$ is still better for high frequencies due
to the strong feedback, the ring topology provides an improvement compared
to the Erdös-Renyi topology when optimizing for $C\ix{high}$.
